---
title: "A1 Analysis in R"
author: "Team 9"
date: "2024-03-09"
output: html_document
---

#### Setting up the environment

Notes: setting up R environment by loading the libraries and installing packages.

## Introduction

The online ticket-selling strategies employed by Air France have proven to be 
effective in augmenting the number of visits to their website, with Media Contacts 
playing a pivotal role in achieving this outcome. As competition intensifies 
and prices escalate, the duty is on Media Contacts to leverage their expertise 
in marketing data analysis to optimize the returns on Air France's investments. 
A thorough data-driven analysis, complemented by visualizations, was conducted 
to discern the strengths and weaknesses of the campaign results, thereby 
enabling the Marketing and Financial teams to make informed decisions on the 
utilization of the insights and recommendations provided.

Numerical outputs and visualizations were developed, adhering to the principle 
that "Without this visual analytics solution, one would be stuck analyzing enormous 
amounts of data in spreadsheets. Instead, the dashboards provide clear actionable 
insights that drive the business forward." (Lay)The focus was predominantly on 
the financial ramifications of the strategies. To this end, outputs were generated, 
such as the Return on Investment (ROI), which facilitated the understanding and 
visualization of the profitability of each investment by comparing the gain or 
loss to its cost and assessing the return on investments. 
(Beattie, 2024)Additionally, an output that depicted the Conversion Rate between 
clicks and bookings was devised, accompanied by a respective Bar Chart, 
to enhance comprehension of each search engine's performance.

Search Engine Marketing (SEM) inherently involves bidding on keywords pertinent 
to the advertised business, thereby rendering keyword research a vital component 
for targeting the desired audience. (Ooi, 2023) By identifying keywords relevant 
to their business, companies can craft effective ads that will appear when users 
search for those keywords. Consequently, a focus was placed on word performance, 
analyzing the different match types of word categories that resulted in bookings.


```{r}
# Install and load necessary packages 
install.packages("tidytext",repos = 'http://cran.us.r-project.org' )
install.packages("stringr",repos = 'http://cran.us.r-project.org' )
install.packages("syuzhet",repos = 'http://cran.us.r-project.org')
install.packages("textdata",repos = 'http://cran.us.r-project.org' )
install.packages("DT", repos = 'http://cran.us.r-project.org')
library(dplyr)
library(ggplot2)
library(wordcloud2)
library(tidyverse)
library(tm)
library(tidytext)
library(stringr)
library(syuzhet)
library(textdata)
library(DT)

# Setting up the current working directory
getwd()
setwd("C:\\Users\\Initha\\OneDrive\\Documents\\Business Challenge II")
getwd()

# Reading the CSV file
data <- read.csv("case_data.csv")

# Display first few rows
head(data, 4)

# Display the structure of the data
str(data, 4)

# Removing dollar sign from the variables
data$Search.Engine.Bid<-gsub("\\$","",data$Search.Engine.Bid)
data$Click.Charges<-gsub("\\$", "",data$Click.Charges)
data$Avg..Cost.per.Click<-gsub("\\$","",data$Avg..Cost.per.Click)
data$Total.Cost..Trans.<-gsub("\\$","",data$Total.Cost..Trans.)
data$Amount <-gsub("\\$","",data$Amount)
data$Total.Cost <-gsub("\\$","",data$Total.Cost)

# Removing percentage sign from the variables
data$Engine.Click.Thru..<-gsub("\\%","",data$Engine.Click.Thru..)
data$Trans..Conv...<-gsub("\\%","",data$Trans..Conv...)

# Removing commas from the variables
data$Clicks<-gsub(",", "",data$Clicks)
data$Click.Charges<-gsub(",", "",data$Click.Charges)
data$Impressions <-gsub(",","",data$Impressions)
data$Total.Cost..Trans.<-gsub(",","",data$Total.Cost..Trans.)
data$Amount <-gsub(",","",data$Amount)
data$Total.Cost <-gsub(",","",data$Total.Cost)

# Checking for the missing values if any in the data
sum(is.na(data))

# Checking for the incomplete cases in the data
data[!complete.cases(data),]

#changing datatype from character to numeric
data$Search.Engine.Bid <- as.numeric(data$Search.Engine.Bid)
data$Clicks<-as.numeric(data$Clicks)
data$Click.Charges <-as.numeric(data$Click.Charges)
data$Avg..Cost.per.Click<-as.numeric(data$Avg..Cost.per.Click)
data$Impressions <-as.numeric(data$Impressions)
data$Engine.Click.Thru.. <-as.numeric(data$Engine.Click.Thru..)
data$Trans..Conv... <-as.numeric(data$Trans..Conv...)
data$Total.Cost..Trans. <-as.numeric(data$Total.Cost..Trans.)
data$Amount <-as.numeric(data$Amount)
data$Total.Cost <-as.numeric(data$Total.Cost)
data$Total.Volume.of.Bookings <-as.numeric(data$Total.Volume.of.Bookings)

str(data, 4)

# Checking null values
sum(is.na(data))

```


```{r}

# Output 1

# replace the blanks values in Bid Strategy as "NO BID"
data[data$Bid.Strategy== "", "Bid.Strategy"] <- "NO BID"
data[data$Bid.Strategy== "", "Bid.Strategy"]
head(data$Bid.Strategy, 4)

```


#### Output 1

Making sure that 'Bid.Strategy' column in the data has no blank values. 
Replacing blanks with "NO BID" provides a clear, definitive label for entries 
without a specified bidding strategy. This line enhances data integrity and makes 
it easy to interpret 'Bid.Strategy' column.This brings consistency which is crucial 
for filtering and analysis. Identifying and labeling entries as "NO BID" could reveal 
how often and under what circumstances bid strategies are not specified. 
This insight could lead to strategic adjustments, such as identifying opportunities for optimization.


```{r}

# Output 2

# replace the NA values in match type as "NOT SPECIFIED"
data[data$Match.Type == "N/A", "Match.Type"] <- "Not Specified"
data[data$Match.Type== "N/A", "Match.Type"]
head(data$Match.Type, 4)

```


#### Output 2

The code looks through the Match Type column to search for all rows with N/A. 
A new variable called "Not Specified" is also created. The new variable is set 
to replace all N/A in Match Type. This is to preprocess the data by replacing 
missing or placeholder values ("N/A") with a more descriptive label ("Not Specified"). 
This to ensure the data do not have ambiguous values, which could affect data analysis.


```{r}

# Output 3

# Summary statistics of numeric fields
data_statistics <- summary(select(data, where(is.numeric)))
print(head(data_statistics, 5))

```


#### Output 3

This is a quick statistical summary of all numeric fields in the data. 
It includes measures of central tendency (mean, median) and dispersion for 
each numerical column. Such statistics are crucial for understanding the 
distribution and scale of our data, helping us identify any outliers or 
anomalies that may affect the analysis. All these numeric columns will 
determine the cost and revenue analytically process of the analysis. 


```{r}

# Visualization 1

#Creating box plots for Publisher and their Average cost for each clicks
publisher_avg_cost <- ggplot(data = data, aes(x = Publisher.Name, 
                                              y = Avg..Cost.per.Click))
publisher_avg_cost + geom_boxplot()

```


#### Visualization 1

The box plot shows the average cost per click for different publishers, such as Google and Yahoo. It highlights:

1.	The price publisher pays for each click varies greatly depending on the company 
whether the ads are run Globally or only in the United States.

2.	Google generally charges more per click than MSN or Overture.

3.	Overture frequently charges the lowest cost per click, in the United States. 

4.	The horizontal line in the center of each box indicates the median cost, 
higher the median more expensive the cost.

5.	There are some cases where clicks are significantly less or more expensive than average. 

6.	Each publisher has outliers, with Google Global having especially expensive outliers.

7.	The cost of clicks varies depending on the organization. 

This data helps businesses in decide where to place their advertisements in order 
to achieve the highest return on investment.


```{r}

# Visualization 2

# Calculating Cost per Click per Publisher Name
publisher_cpc <- data %>%
  group_by(Publisher.Name) %>%
  summarize(Total_Cost = sum(Total.Cost), Total_Clicks = sum(Clicks), 
            CPC = ifelse(Total_Clicks > 0, Total_Cost / Total_Clicks, 0)) %>%
  arrange(desc(CPC))

# Creating the bar chart for Cost per Click
ggplot(publisher_cpc, aes(x = reorder(Publisher.Name, -CPC), y = CPC)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Publisher Name", y = "Cost per Click (CPC)", 
       title = "Cost per Click by Publisher")

```


#### Visualization 2

The bar chart shows average cost per click (CPC) for publishers. It highlights:

1.	Google Global has the highest average cost-per-click, with more than 1.5 (CPC).

2.	Google US follows closely with the second highest CPC.

3.	MSN US has a somewhat high CPC, which is lower than the two Google categories.

4.	CPCs for Overture US and MSN Global are similar, falling in the lower middle range.

5.	Overture Global has a lower cost per click (CPC) than Overture US and MSN Global.

6.	Yahoo US has the lowest CPC of the publishers listed. 

The chart clearly shows CPC pricing differences amongst publishers that may 
influences marketers. Advertisers may select Yahoo US for the most cost-effective clicks. 
Google's services, while more expensive, may have a wider reach or perceived value.
This data can help advertisers in budgeting campaigns and selecting cost-effective platforms.


```{r}

# Visualization 3

# Aggregate and Sum Bookings by Publisher
agg_book <- aggregate(Total.Volume.of.Bookings~Publisher.Name, data = data, FUN = sum)
agg_book <- agg_book[order(-agg_book$Total.Volume.of.Bookings), ]

# Creating bar chart for publisher and the booking
ggplot(data = agg_book, aes(x = reorder(Publisher.Name, -Total.Volume.of.Bookings), 
                            y = Total.Volume.of.Bookings)) +
  geom_bar(stat = "identity") +
  labs(x = "Publisher Name", y = "Total Volume of Bookings", 
       title = "volume of Bookings for various Publishers")

```


#### Visualization 3

The bar chart shows the overall volume of bookings for various publishers. 
The graphic provides a simple way to compare booking volumes across different 
publishers and markets, representing that Google - US leads this statistic. It highlights:

1.	Google - US has the largest overall volume of bookings, approaching 1500.

2.	Yahoo - US comes in second, with slightly more than half the volume of Google - US.

3.	Google - Global ranks third, with a somewhat lower overall volume than Yahoo - US.

4.	Overture - US ranks fourth, closely followed by Overture - Global.

5.	MSN - US and MSN - Global had the lowest total number of bookings among the 
listed publishers, with MSN - Global having the fewest.

In the bars for "US" market publishers are often higher than their "Global" 
competitors, which could indicate that these publishers perform better or have 
a stronger presence in the US market.


```{r}

# Output 4

# Count of Publishers
Publishers <- length(unique(data$Publisher.Name))
print(paste("Publishers:", Publishers))

```


#### Output 4

The analysis is about individual Publishers in the data. This will aid in determining 
the effectiveness and reach of the Publishers' skills, as well as their consumer 
involvement. Unique function is attached to the Publisher Name so that Publishers' 
name that appears more than once, will not be counted more than one. 
Length function is attached to the unique Publishers' name so that it counts the 
total instead of listing. The insights are going to be based on Publisher's result
so knowing their total is a way to go.


```{r}

# Visualization 4

# Aggregate and Sum Clicks by Publisher:
agg_clicks <- aggregate(Clicks~Publisher.Name, data = data, FUN = sum)
agg_clicks <- agg_clicks[order(-agg_clicks$Clicks), ]

#Bar chart for publisher and the clicks
ggplot(data = agg_clicks, aes(x = reorder(Publisher.Name, -Clicks), 
                                    y = Clicks)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Publisher Name", y = "Clicks", 
       title = "Clicks for each Publishers")

```


#### Visualization 4

The bar chart shows the clicks for several publishers from both the US and global 
markets. Clicks are tracked for Google-US, Overture-US, Google-Global, Yahoo-US, 
Overture-Global, MSN-US, and MSN-Global. It highlights:

1.	Google – US received the most clicks, with the bar reaching more than 150,000, 
showing a large lead over the other publishers.

2.	Overture - US comes in second, but with fewer than two-thirds the number of 
clicks as Google - US.

3.	Google - Global is close behind Overture - US, suggesting a large global presence.

4.	Yahoo - US and Overture - Global have comparable click volumes, which are both 
lower than Google - Global but still significant.

5.	MSN - US and MSN - Global had the fewest number of clicks, with MSN - Global having the least.

This could reveal numerous aspects, including Google's dominance in the US market 
and the global success of these publishers. It also demonstrates the huge contrast 
in click volumes between marketplaces and publications.


```{r}

# Visualization 5

# Calculating the ratio of Total Volume of Bookings to Clicks for each publisher
publisher_cr <- data%>%
  group_by(Publisher.Name) %>%
  summarize(Total_Bookings = sum(Total.Volume.of.Bookings), Total_Clicks = sum(Clicks), 
            Booking_Click_Ratio = ifelse(Total_Clicks > 0, Total_Bookings / Total_Clicks, 0)) %>%
  arrange(desc(Booking_Click_Ratio))

# Creating the bar chart
ggplot(publisher_cr, aes(x = reorder(Publisher.Name, -Booking_Click_Ratio), 
                         y = Booking_Click_Ratio)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Publisher Name", y = "Bookings per Click Ratio", 
       title = "Bookings per Click Ratio by Publisher")

```


#### Visualization 5

The bar chart named "Bookings per Click Ratio by Publisher" that compares the 
efficiency of bookings to clicks across various publishers in both the US and 
global markets. It highlights:

1.	Yahoo - US has the best bookings per click ratio, indicating that it converts 
the most clicks into bookings when compared to its click count.

2.	MSN - US comes next, with a slightly lower ratio than Yahoo - US but still 
greater than the rest, demonstrating good market efficiency in the United States.

3.	MSN - Global, Google - Global, and Google - US have successively lower ratios, 
showing that while they receive a lot of clicks, the conversion to bookings is 
not as great as Yahoo - US or MSN - US.

4.	Overture - Global and Overture - US have the lowest bookings per click ratios, 
implying that they may require more clicks to obtain a booking than others.

This measure is frequently used to assess an ad publisher's performance in turning 
clicks into bookings, with greater ratios being considered better. According to 
the bars, some publishers may be more effective globally, while others may flourish 
in the United States.


```{r}

# Output 5

# Total clicks converted to Booking for each Publisher
conversion_rates <- data %>%
  group_by(Publisher.Name) %>%
  summarise(Total_Clicks = sum(Clicks, na.rm = TRUE),
            Total_Bookings = sum(Total.Volume.of.Bookings, na.rm = TRUE),
            Conversion_Rate = (Total_Bookings / Total_Clicks) * 100) %>%
  arrange(desc(Conversion_Rate))

# Display the conversion rates
print(conversion_rates)

```


#### Output 5

This code is created to give an overview of the rate at which each Publishers, 
clicks turns to booking. This shows how each cost the client pays for each click 
for every publisher turns to revenue to the client. Total bookings were divided by 
total clicks to show the rate clicks are converted. This shows how effective publishers 
have been able to push adverts to the right customers. This have been arranged in 
descending order for proper analysis. The results showed that Yahoo - US gave a 
higher conversion rate of 1.45%. Meaning that 1.45% of every click we pay for turns 
into booking which is the primary aim for business.


```{r}

# Output 6

# Calculate Net Returns (Amount - Total Cost) by Publisher
net_returns_publisher <- data %>%
  group_by(Publisher.Name) %>%
  summarise(
    # Calculate net returns for each publisher
    Net_Returns = sum(as.numeric(Amount)) - sum(as.numeric(Total.Cost)) 
  ) %>%
  # Arranging in descending order of net returns for fast analysis
  arrange(desc(Net_Returns))  

# Display Results
print(net_returns_publisher)

```


#### Output 6

This code is created to give an overview of the total returns received from the 
investment in advertising with each Publisher. This shows the revenue generated from 
each Publisher. This has been calculated as the Amount received less the cost for 
each Publisher. This will be a metric in the analysis to determine whether the investment 
is been optimized. This have been arranged in descending order for proper analysis. 
From the results, it is seen that Google - US is giving a Net Returns of $1,316,772 
followed by Yahoo _ US with $832,648. the next output will be to show if these results 
are based on conversion rates or just because there were a lot of adverts placed that 
brought out that returns. Further analysis will be conducted for investment optimization.


```{r}

# Visualization 6

# Calculating ROI per Publisher Name
publisher_roi <- data %>%
  group_by(Publisher.Name) %>%
  summarize(Total_Amount = sum(Amount), Total_Cost = sum(Total.Cost), 
            ROI = ifelse(Total_Cost > 0, (Total_Amount - Total_Cost) / Total_Cost, 0)) %>%
  arrange(desc(ROI))

# Creating the bar chart for ROI
ggplot(publisher_roi, aes(x = reorder(Publisher.Name, -ROI), y = ROI)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Publisher Name", y = "ROI", title = "ROI by Publisher")

```


#### Visualization 6

The bar chart labelled "ROI by Publisher" that calculates the Return on Investment (ROI) 
for various publishers. It highlights:

1.	Yahoo - US has the greatest ROI, with a number greater than 15, suggesting 
that investing in Yahoo's US advertisements yields much larger returns than other publishers.

2.	MSN - Global and MSN - US come next, with MSN - Global marginally outperforming 
MSN - US, indicating a good ROI for these areas.

3.	Google - Global has a ROI of about 5, which is moderate compared to the others, 
whereas Google - US is slightly lower, indicating a poorer return per investment in these regions.

4.	Overture - Global has a ROI that is around half that of Google, indicating 
inferior investment efficiency.

5.	Overture - US has the lowest ROI on the chart, implying that investing in 
Overture's US ads yields the lowest return compared to the others.

The chart indicates which publishes and markets may generate higher financial 
returns on advertising spend. Advertisers must take such data into account when 
developing marketing strategy.


```{r}

# Output 7

# Display calculated value
publisher_roi

```


#### Output 7

Publishers' ROI represents the Return on Investment. This shows how much the client 
gets in return for every dollar it invest in advertising with each Publisher. This 
is calculated as the Revenue divided by Total cost incurred in getting that Revenue. 
This gives a fair idea in the analysis, which investment in a Publisher was giving best 
optimization. It has been arranged in order to ease in the analysis. It can be seen from 
the output that Yahoo - US gave a higher Return on Investment (ROI) of $18.20 which is 
about $14 higher than Google - US which gave a higher Net Return. This shows that investing 
more in advertisement with Yahoo - US will be a very good decision.


```{r}

# Visualization 7

# Checking summary and the structure of the match type
summary(data$Match.Type)
str(data$Match.Type)

# Plotting histogram of match type for the keywords
# Creating a bar chart
mat_typ <- ggplot(data= data, aes(x= Match.Type))
mat_typ + geom_bar() +
  labs(x = "Match Type", y = "Count", title = "Number of Match Type")

```


#### Visualization 7

The bar chart displaying the count of various match types: Advanced, Broad, 
Exact, Not Specified, and Standard. It highlights:

1.	Broad match types have the largest count, with the bar exceeding 2000, 
indicating that they are the most common or frequently occurring keywords in the data.

2.	Advanced and Standard have significantly lower counts than Broad, with Advanced 
marginally outperforming Standard.

3.	The Exact match type has a very low count compared to the others, indicating 
that it is the least popular or frequently used match type in this data.

4.	Not Specified has no bar, indicating that there are no occurrences or that the count is minimal.

This may indicate that when selecting a match type, the preference or effectiveness 
may tilt strongly towards "Broad" match, depending on the context in which these 
match types are used. Exact matches are rarely used, possibly because of their 
limited nature. The absence of "Not Specified" could indicate that data in this 
data is generally adequately categorized.


```{r}

# Visualization 8

# Creating a bar chart
rev<- ggplot(data= data, aes(x= Publisher.Name, y= Amount)) +
  geom_bar(stat="identity") + 
  labs(x = "Publisher Name", y = "Amount", title = "")
rev

```


#### Visualization 8

The bar chart that depicts the amounts linked with various publishers, 
distinguishing between worldwide and US marketplaces. It highlights:

1.	Google - US has the most by a substantial margin, greatly exceeding others, 
showing a strong position in terms of the parameter being measured (revenue, ad expenditure, and so on).

2.	Google - Global is the second highest, but only about a third of the amount 
of Google US, indicating that Google's US market is significantly greater for this metric.

3.	MSN - Global and MSN – US have nearly similar amounts, with MSN - Global 
somewhat greater, indicating a balanced performance throughout these markets.

4.	Overture – Global and Overture - US have the smallest amounts, with Overture - US 
slightly higher than the global counterpart.

5.	Yahoo - US is much higher than MSN and Overture, but much lower than Google.

The distribution demonstrates Google's dominance, notably in the United States, 
and implies that Yahoo, while not at Google's level, holds a solid position in 
comparison to MSN and Overture. The close numbers for MSN global and US 
presence may reflect consistent success across markets.


```{r}

# Visualization 9

# Creating a bar chart
amt_spnd <- ggplot(data= data, aes(x= Publisher.Name, y= Total.Cost)) +
  geom_bar(stat="identity") +
  labs(x = "Match Type", y = "Count", title = "Number of Match Type")
amt_spnd

```


#### Visualization 9

The bar chart depicting the "Total Cost" connected with various publishers, 
with a logarithmic scale on the y-axis, as indicated by the "3e+05" style notation, 
which reflects amounts in the hundreds of thousands. It highlights:

1.	Google - US has the highest overall cost by a large margin, indicating that 
this publisher has made a considerable investment in the US market.

2.	Google - Global has the second-highest costs, although they are less than 
half of those for Google - US, implying that Google's US operations may be more 
cost-intensive or that spending is higher in the United States.

3.	The costs of MSN - worldwide and MSN - US are similar, with the worldwide 
costs slightly higher.

4.	Overture - Global and Overture - US have the lowest expenses on the chart, 
with US costs somewhat higher than global.

5.	Yahoo - US has noticeable costs, which are much lower than Google but higher 
than MSN and Overture's.

The use of a logarithmic scale indicates a large range of values and aids 
in comparing costs between publishers. The statistics may indicate where market 
investment priorities lay or where the majority of resources are being directed.


```{r}

# Visualization 10

## word cloud
names(data)[names(data) == 'Keyword'] <- 'text'

wld_cld <- VCorpus(VectorSource(data$text))
wld_cld <- tm_map(wld_cld, content_transformer(tolower))  # convert to lower case
wld_cld <- tm_map(wld_cld, removePunctuation)             # remove punctuation
wld_cld <- tm_map(wld_cld, removeNumbers)                 # remove numbers
wld_cld <- tm_map(wld_cld, stripWhitespace)               # remove redundant spaces

tidy_text <- tidy(wld_cld)
tidy_text <- data %>%
  mutate(row = row_number()) %>%
  unnest_tokens(word, text)

print(colnames(tidy_text))
print(colnames(stop_words))

tidy_text <- tidy_text %>%
  anti_join(stop_words, by = "word")

word_freq <- tidy_text %>%
  count(word, sort = TRUE)
print(head(word_freq, 4))

wordcloud2(word_freq,
           color='random-light',
           shape = 'cloud',
           rotateRatio = 1)

```


#### Visualization 10

The word cloud, which is a visual representation of text data in which the size 
of each word represents its frequency or relevance. Travel-related terms, 
notably flights and air travel, dominate this word cloud. 
Important findings from the word cloud:

1.	The word "flight" and "cheap" are the most common, implying a heavy emphasis 
on low-cost air travel.

2.	The titles of various European cities and countries, such as "France," 
"Paris," "Rome," "Italy," and "Europe," reflect a concentration on this region.

3.	Words like "Tickets," "Fares," "Airfare," and "Discount" are also used frequently, 
highlighting the cost of air travel.

4.	The appearance of the word "Airline" alongside specific cities shows that 
the data is related to searches or discussions regarding airlines that serve these areas.

5.	The term "airport" and the names of specific cities denote a possible study 
of air travel routes or destinations.

Overall, the word cloud appears to indicate subjects connected to searching for 
or discussing economical flight.


```{r}

# Output 8

# Defining a data frame named kayak_tab
kayak_tab <- data.frame(
  Search_Engine = "Kayak",
  Clicks = 2839,
  Media_Cost = 3567.13,
  Total_Bookings = 208,
  Avg_Ticket = 1123.53,
  Total_Revenue = 233694.00,
  Net_Revenue = 230126.87,
  stringsAsFactors = FALSE
)

# Display an interactive table with DT
datatable(kayak_tab, options = list(pageLength = 5, scrollX = TRUE))

# Display kayak data as a tabular output
print(kayak_tab)

```


#### Output 8

Clicks (2839), this metric indicating a reasonable degree of user participation. 
Media Cost ($3567.13), the total campaign budget. Total Bookings (208), number of successful 
transactions resulting from clicks. Average Ticket ($1123.53), high revenue suggests a 
premium offering or numerous items per transaction. Total Revenue ($233694.00) is the campaign's 
gross income. Net Revenue ($230126.87) profit after deducting ad cost, indicating a very 
successful campaign. Revenue on ads, exceptionally high, with each dollar invested yielding about 
$65.49. Conversion Rate at 7.32%, it demonstrates strong performance in converting clicks 
into bookings. CPA at $17.15 per booking, the campaign is reasonably priced. Overall, 
the data suggests a profitable ad campaign, but this does not account for other operating expenditures.


```{r}

# Output 9

# Calculate Cost Per Click for each publisher
Cost_per_Click_Publisher <- data %>%
  group_by(Publisher.Name) %>%
  summarise(
    Total_Cost = sum(as.numeric(Total.Cost), na.rm = TRUE),  
    # Sum up clicks, also ignoring NA values
    Total_Clicks = sum(Clicks, na.rm = TRUE),  
    # Calculate CPC; avoid division by zero by setting CPC to NA when no clicks are present
    Cost_Per_Click = ifelse(Total_Clicks > 0, Total_Cost / Total_Clicks, NA)  
  ) %>%
  arrange(desc(Cost_Per_Click)) 

# Display the calculated Cost-Per_Click for each publisher
print(Cost_per_Click_Publisher)

```


#### Output 9

This operation is aimed at evaluating the cost efficiency of clicks across different 
publishers. After knowing the Net Returns and Return on Investment by Publishers, 
knowing cost per click for each publisher will help the analyse how to place advertisement 
with the publishers that will give the desired bookings whiles controlling or reducing 
the cost associated thereof. This has calculated by dividing the total cost by the 
total clicks by each publisher to determine cost per click. The lower the cost per click, 
the better. However, that will be conclusive if the lower clicks are leading to higher 
bookings and higher returns on investment. Yahoo - US have the lowest cost per click of 
$1.01, followed by MSN - Global with $1.10 and Google – Global Google - US having 
$1.89 and $1.84 respectively.


```{r}

# Output 10

# Calculating metrics by Match Type
Match_type_metrics <- data %>%
  group_by(Match.Type) %>% 
  summarise(
    Total_Clicks = sum(Clicks, na.rm = TRUE),
    Total_Impressions = sum(Impressions, na.rm = TRUE),
    Total_Bookings = sum(Total.Volume.of.Bookings, na.rm = TRUE),
    Conversion_Rate = (Total_Bookings / Total_Clicks) * 100
  ) %>%
  mutate(Conversion_Rate = ifelse(is.nan(Conversion_Rate), 0, Conversion_Rate)) # Replace NaN with 0 in case of division by zero

# Display the calculated metrics
print(Match_type_metrics)

```


#### Output 10

In Search Engine Marketing and Optimization, keywords play active role and must be 
selected carefully. For this reason, the analysis focuses on keyword analysis in the 
match type category. The goal of keyword match type analysis is to establish which 
match types used in advertisements result in the most bookings, while keeping in mind 
that the goal is to generate bookings rather than clicks. This can help you understand 
how different match types affect overall campaign performance, identifying areas where 
you may improve conversion rates and effectiveness through optimization. The results 
revealed that exact match types had the greatest conversion rate of 1.48. 
As a result, it is recommended that you employ exact match keywords.


## Top three actionable insights

Through the analytically processes have extracted pivotal findings:

1. The expenditure analysis highlights that a significant portion of the 
search engine marketing budget is allocated to Google - Global and Google - US. 
These platforms, while generating the highest click-through (180,208 clicks) 
and booking volume, exhibit modest returns on investment (ROI)—4.95 for Google - Global 
and 3.96 for Google - US.It is suggested that the Finance and Marketing teams collaborate 
to refine the budget allocation for these platforms to enhance efficiency and optimize ROI. 

2. An in-depth ROI analysis indicates a standout performance by Yahoo as the 
search engine marketing channel, yielding an ROI of 18.22. Despite only 7.63% 
of the search engine marketing budget being directed towards Yahoo, it delivers 
the most favorable conversion rate at 1.45 and maintains the lowest cost per 
click at $1.01. It is advised to redirect funds from Google to Yahoo, 
anticipating improved outcomes without escalating the overall marketing spend.

3. The keyword strategy assessment reveals that 'Broad' match type predominates 
the usage, with 45,294 instances leading to 236,914 impressions and 672 bookings. 
This match type achieves the highest conversion rate at 1.48 compared to its 
counterparts. Data underscores the strategic advantage of targeting precise 
keywords to maximize conversion efficiency. The Marketing team is encouraged 
to utilize the Word Cloud for a granular analysis to determine the most 
impact keywords for our campaigns, prioritizing high-conversion keywords 
and eliminating or reducing spending on low-performing keywords. 


## Conclusion

In conclusion, Yahoo has been identified as the most cost-effective search engine 
in terms of cost per click and return on investment, positioning it as the optimal 
choice for AirFrance. It is advisable for AirFrance to reallocate a portion of 
its budget from Google to Yahoo, thereby enhancing revenue optimization without 
increasing the overall investment. To ensure the effectiveness of this strategy, 
it is recommended that the results be monitored on a monthly basis to maintain 
a record of the strategy's performance.


## Bibliography
Beattie, A. (2024, 2 28). ROI: Return on Investment Meaning and Calculation Investopedia. 
Retrieved from 
<https://www.investopedia.com/articles/basics/10/guide-to-calculating-roi.asp>

Lay, D. (n.d.). A Guide To Data Driven Decision Making: What It Is, Its Importance, & How To Implement It. 
Retrieved from tableau: 
<https://www.tableau.com/learn/articles/data-driven-decision-making>

Ooi, J. (2023, 08 18). The Importance of Keyword Research in SEM: Maximizing Your Online Visibility. 
Retrieved from nightowl: 
<https://nightowl.sg/blog/the-importance-of-keyword-research-in-sem-maximizing-your-online-visibility/>





